Supplementary Material

### 2013-10-04 icml/boosted-mirror-descent.tex
draft of connections subsection

Mirror descent, together with boosting, yields an algorithm for finding 
``saddle points'' of $L$. 
For notational convenience, for a sequence of weights $\alpha_1,\alpha_2,\ldots$ 
let $\hat{u}_t = \frac{\sum_{s=1}^t \alpha_su_s}{\sum_{s=1}^t \alpha_s}$ and let 
$\hat{\theta}_t = \frac{\sum_{s=1}^t \alpha_s\theta_s}{\sum_{s=1}^t \alpha_s}$. Then 
the {\em primal boosted mirror descent} (\primal) algorithm is:
\begin{enumerate}
\item $u_1 \in \arg\min_u h(u)$
\item $\theta_{t} \in \arg\max_{\theta \in \Theta} \langle \theta, u_t \rangle - R(\theta) = \partial R^{*}(u_{t})$
\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \hat{\theta}_t, u \rangle = \partial h^{*}(-\hat\theta_{t})$
\end{enumerate}
As long as $h$ is strongly convex, we obtain the 
bound (see Corollary~\ref{cor:method-1}):
\begin{equation}
\sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq L_{*} + O(1/T).
\end{equation}
In other words, $\hat{u}_T$ is close to being a global minimum of $L(u)$.
However, it is often the case that $h$ is not strongly convex, whereas $R$ is strongly convex. As we shall see, this will be the case for our application to herding.
In this case we may wish to use the following slightly different algorithm, which we call {\em dual boosted mirror descent} (\dual):
\begin{enumerate}
\item $\theta_1 \in \arg\min_{\theta} R(\theta)$
\item $u_t \in \arg\min_{u} h(u) + \langle \theta_t, u \rangle = \partial h^{*}(-\theta_{t})$
\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \hat{u}_t \rangle - R(\theta) = \partial R^{*}(\hat u_{t})$
\end{enumerate}
We then obtain the following bound 
when $R$ is strongly convex (see Corollary~\ref{cor:method-2}):
\[ \sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq L_{*} + O(1/T). \]
As suggested by the name \primal and \dual are closely related; indeed, they are dual to each other in the sense that 
performing \primal on $L(u,\theta)$ is the same as performing \dual on 
$-L(\theta,u)$.

@@

The \bmd algorithms are very closely related to \cgd and \md.

\end{document}

>>>>

Mirror descent, together with boosting, yields an algorithm for finding 
``saddle points'' of $L$. 
For notational convenience, for a sequence of weights $\alpha_1,\alpha_2,\ldots$ 
let $\hat{u}_t = \frac{\sum_{s=1}^t \alpha_su_s}{\sum_{s=1}^t \alpha_s}$ and let 
$\hat{\theta}_t = \frac{\sum_{s=1}^t \alpha_s\theta_s}{\sum_{s=1}^t \alpha_s}$. Then 
the {\em primal boosted mirror descent} (\primal) algorithm is:
\begin{enumerate}
\item $u_1 \in \arg\min_u h(u)$
\item $\theta_{t} \in \arg\max_{\theta \in \Theta} \langle \theta, u_t \rangle - R(\theta) = \partial R^{*}(u_{t})$
\item $u_{t+1} \in \arg\min_{u} h(u) + \langle \hat{\theta}_t, u \rangle = \partial h^{*}(-\hat\theta_{t})$
\end{enumerate}
As long as $h$ is strongly convex, for the proper choice of $\alpha_{t}$ we obtain the 
bound (see Corollary~\ref{cor:method-1}):
\begin{equation}
\sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq L_{*} + O(1/T).
\end{equation}
In other words, $\hat{u}_T$ is close to being a global minimum of $L(u)$.
However, it is often the case that $h$ is not strongly convex, whereas $R$ is strongly convex. As we shall see, this will be the case for our application to herding.
In this case we may wish to use the following slightly different algorithm, which we call {\em dual boosted mirror descent} (\dual):
\begin{enumerate}
\item $\theta_1 \in \arg\min_{\theta} R(\theta)$
\item $u_t \in \arg\min_{u} h(u) + \langle \theta_t, u \rangle = \partial h^{*}(-\theta_{t})$
\item $\theta_{t+1} \in \arg\max_{\theta \in \Theta} \langle \theta, \hat{u}_t \rangle - R(\theta) = \partial R^{*}(\hat u_{t})$
\end{enumerate}
We then obtain the following bound 
when $R$ is strongly convex (see Corollary~\ref{cor:method-2}):
\[ \sup_{\theta \in \Theta} L(\hat{u}_T, \theta) \leq L_{*} + O(1/T). \]

@@

As suggested by their names, the \bmd algorithms are closely related: they are dual to each other in the sense that 
performing \primal on $L(u,\theta)$ is the same as performing \dual on $-L(\theta,u)$. This relationship is obvious by inspection of the update equations:
\(
\text{Primal} && \text{Dual} \\
\theta_{t} &= \partial R^{*}(u_{t}) & \theta_{t+1} &= \partial R^{*}(\hat u_{t}) \\
u_{t+1} &= \partial h^{*}(-\hat\theta_{t}) & u_t &= \partial h^{*}(-\theta_{t})
\)
This duality is analogous to that between mirror descent and conjugate gradient descent \citep{Bach:2012b}. \md minimizes $g(x) + f(x)$ and requires that $g$ be $\alpha$-strongly convex while \cgd minimizes $g^{*}(x) + f^{*}(x)$ and requires that $g$ be $\alpha$-strongly convex. The update equations are
\(
y_{t} &= \partial f(x_{t})  \\
\bar y_{t} &=  (1 - \rho_{t+1})\partial g(x_{t}) - \rho_{t+1}y_{t}  \\
x_{t+1} &=  \partial g^{*}(\bar y_{t}) 
\)
for \md and
\(
 y_{t+1} &= \partial f(x_{t}) \\
\bar y_{t+1} &= (1 - \rho_{t})\bar y_{t} + \rho_{t} y_{t+1}  \\
x_{t} &= \partial g^{*}(-\bar y_{t})
\)
for \cgd. 
In fact, the \bmd algorithms are very closely related to \cgd and \md: \cgd can be obtained from \dual and \md obtained from \primal. The relationships are given in Table~\ref{tab:connections}. The table also shows how generalized herding and $q$-herding --- which are discussed in the next section --- are obtained from \bmd.

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{table*}[t]
\caption{Formulation of herding and convex optimization algorithms in terms of \bmd. Full details relating \md and \cgd to \bmd are given in the Supplementary Material.}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{L|lllLL}
Algorithm 			& $h(u)$ 	& $R(\theta)$ & $\alpha_{t}$ & \bmd Algorithm & Notes 
\\ \hline
generalized herding & 0			& $\ip{\bar\phi}{\theta} + \frac{1}{2} \| \theta \|_{\sH}^{2}$ 	& unconstrained 	& \dual &
\\ 
$q$-herding			& 0			& $\ip{\bar\phi}{\theta} + \frac{1}{q} \| \theta \|_{q}^{q}$ 	& unconstrained 	& \dual & $q \ge 2$
\\ 
\md					& $g(x)$	& $f^{*}(y)$				& $\rho_{t}/\prod_{s=1}^{t} (1 - \rho_{s})$				& \primal & 
\\ 
\cgd				& $f^{*}(y)$& $g(x)$					& $\rho_{t}/\prod_{s=1}^{t} (1 - \rho_{s})$				& \dual &
\\
\end{tabularx}
\label{tab:connections}
\end{table*}
\end{center}
\end{document}

### 2013-10-04 icml/introduction.tex
draft of connections subsection

Since its introduction, herding has been shown to have many desirable properties.
For instance, Chen et al showed that the moments converge at a rate of $O(1/T)$ for 
$T$ samples, which is even faster than the $O(1/\sqrt{T})$ that would be obtained 
by sampling the exact posterior. Furthermore, Bach et al show that herding is 
equivalent to conditional gradient, and Husz\'{a}r and Duvenaud show that 
herding is Bayesian quadrature. Herding was originally conceived of as a method 
for inference in MRF, and this line of work has been further explored in 
\citet{Welling:2009a,Gelfand:2010,Bornn:2013}.

In order to define herding, let $\sX$ be an observation space, $\phi : \sX \to \sB_{\Theta}$ a 
feature map to an inner product space, and $\bar\phi = \bE_{x \sim p}[\phi(x)]$ the empirical 
moments of some distribution. Then the herding algorithm is the following simple procedure to 
generate pseudosamples from $\sX$:
\[
x_{t} &\in \argmin_{x \in \sX} \ip{\theta_{t}}{\phi(x)} \\
\theta_{t} &= \theta_{t-1}  + \bar \phi - \phi(x_{t}).
\]
In this paper we generalize the herding algorithm to the following set of updates, which 
require only the convexity of $h$ and $R$:
\[
u_t &\in \argmin_{u} h(u) + \ip{\theta_t}{u} \\
\theta_{t+1} &\in \argmax_{\theta} \ip{\theta}{\hat{u}_t} - R(\theta),
\]
where $\hat{u}_t$ is a certain weighted average of $u_1,\ldots,u_t$. Our 
algorithm is described in more detail in Section~\ref{sec:algorithm}. This 
generalization has several advantages:
\begin{itemize}
\item It allows us to cast herding in the framework of mirror descent, 
      which lets us better understand its convergence properties.
\item It allows us to obtain generalizations of herding for infinite 
      dimensional spaces that may apply even if standard herding does not.
\item It makes the known connections between herding, subgradient, and 
      conditional gradient methods more clear. 
\end{itemize}
In particular, while it was known that herding was a form of conditional 
gradient \cite{TODO} and hence (via the relationship in \cite{TODO}) also 
a form of subgradient descent, our framework exposes all three algorithms 
as special cases. A full table of the relationships for various choices of 
$h$ and $R$ is given in Figure~\ref{fig:table}.
% -- Doesn't seem relevant enough to justify the amount of technical detail
%An alternative interpretation of herding \citep{Chen:2010a,Huszar:2012,Bach:2012a} is as a moment matching algorithm. In particular, it generates a set of pseudosamples $\{ x_{t} \}$  which match the moments $\bar\phi$. That is, the squared error $\sE_{T}^{2} \eqdef \| \bar\phi - T^{-1}\sum_{t=1}^{T} \phi(x_{t})\|^{2} \to 0$ as $T \to \infty$.  If $\sB_{\Theta}$ is a reproducing kernel Hilbert space (RKHS) with feature map $\phi$, $\sE_{T}^{2}$ is equivalent to the maximum mean discrepancy (MMD) between $p$ and the empirical distribution $\hat p_{T} \eqdef T^{-1}\sum_{t=1}^{T} \delta_{x_{t}}$ \citep{Huszar:2012}:
%\(
%\sE_{T}^{2} &= \MMD^{2}(p, \hat p_{T})  \\
%&\eqdef \sup_{\theta \in \Theta} \left|\bE_{p}\ip{\theta}{\phi(x)} - \bE_{\hat p_{T}}\ip{\theta}{\phi(x)} \right|,
%\)
%where $\Theta = \{ \theta \in \sB_{\Theta} \ | \  \|\theta\| = 1 \}$.

>>>>

Since its introduction, herding has been shown to have many desirable properties.
For instance, Chen et al showed that the moments converge at a rate of $O(1/T^{2})$ for 
$T$ samples, which is even faster than the $O(1/T)$ that would be obtained 
by sampling the exact posterior. Furthermore, Bach et al show that herding is 
equivalent to conditional gradient, and \citet{Huszar:2012} show that 
herding is Bayesian quadrature. Herding was originally conceived of as a method 
for inference in MRF, and this line of work has been further explored in 
\citet{Welling:2009a}, \citet{Gelfand:2010} and \citet{Bornn:2013}.

In order to define herding, let $\sX$ be an observation space, $\phi : \sX \to \sB_{\Theta}$ a 
feature map to an inner product space, and $\bar\phi = \bE_{x \sim p}[\phi(x)]$ the empirical 
moments of some distribution. Then the herding algorithm is the following simple procedure to 
generate pseudosamples from $\sX$:
\[
x_{t} &\in \argmin_{x \in \sX} \ip{\theta_{t}}{\phi(x)} \\
\theta_{t} &= \theta_{t-1}  + \bar \phi - \phi(x_{t}).
\]
In this paper we generalize the herding algorithm to the following set of updates, which 
require only the convexity of $h$ and $R$:
\[
u_t &\in \argmin_{u} h(u) + \ip{\theta_t}{u} \\
\theta_{t+1} &\in \argmax_{\theta} \ip{\theta}{\hat{u}_t} - R(\theta),
\]
where $\hat{u}_t$ is a certain weighted average of $u_1,\ldots,u_t$. Our 
algorithm is described in more detail in Section~\ref{sec:algorithm}. This 
generalization has several advantages:
\begin{itemize}
\item It allows us to cast herding in the framework of mirror descent, 
      which lets us better understand its convergence properties.
\item It allows us to obtain generalizations of herding for infinite 
      dimensional spaces that may apply even if standard herding does not.
\item It makes the known connections between herding, subgradient, and 
      conditional gradient methods more clear. 
\end{itemize}
In particular, while it was known that herding was a form of conditional 
gradient \cite{Bach:2012a} and hence (via the relationship in \cite{Bach:2012b}) also 
a form of subgradient descent, our framework exposes all three algorithms 
as special cases. A full table of the relationships for various choices of 
$h$ and $R$ is given in Table~\ref{tab:connections}.
% -- Doesn't seem relevant enough to justify the amount of technical detail
%An alternative interpretation of herding \citep{Chen:2010a,Huszar:2012,Bach:2012a} is as a moment matching algorithm. In particular, it generates a set of pseudosamples $\{ x_{t} \}$  which match the moments $\bar\phi$. That is, the squared error $\sE_{T}^{2} \eqdef \| \bar\phi - T^{-1}\sum_{t=1}^{T} \phi(x_{t})\|^{2} \to 0$ as $T \to \infty$.  If $\sB_{\Theta}$ is a reproducing kernel Hilbert space (RKHS) with feature map $\phi$, $\sE_{T}^{2}$ is equivalent to the maximum mean discrepancy (MMD) between $p$ and the empirical distribution $\hat p_{T} \eqdef T^{-1}\sum_{t=1}^{T} \delta_{x_{t}}$ \citep{Huszar:2012}:
%\(
%\sE_{T}^{2} &= \MMD^{2}(p, \hat p_{T})  \\
%&\eqdef \sup_{\theta \in \Theta} \left|\bE_{p}\ip{\theta}{\phi(x)} - \bE_{\hat p_{T}}\ip{\theta}{\phi(x)} \right|,
%\)
%where $\Theta = \{ \theta \in \sB_{\Theta} \ | \  \|\theta\| = 1 \}$.
